\Large Bayes network classifiers for fMRI

### 2012-09-17 proposal/proposal.tex
minor changes in proposal
proposal update

Participants performed an experiment while laying in an fMRI scanner. The experiment consisted of a set of trials in which participants were presented a first stimulus for four seconds, followed by a blank screen lasting four seconds, and then a second stimulus for four seconds, followed by a rest period of 15 seconds. For the first half of the trials, a picture was presented as the first stimulus and a sentence as the second stimulus, while for the second half of trials, a sentence was presented as the first stimulus and a picture as the second. Participants had four seconds after the second stimulus appeared to indicate that the sentence and picture belonged together, after which the stimulus disappeared. If participants did not press a button the stimulus would disappear after four seconds.

@@

\begin{description}
	\item[11th - 21st September]\-\\
	During this time period, the group members will conduct an initial research. The research will focus on the Bayes network classifiers and especially on the TAN tree algorithm.
	\item[22nd - 28th September]\-\\
	During this time period, the definition of the various models will be realised.
	\item[29th - 19th October]\-\\
	Implementation and Parameter estimation.
	\item[20th - 22nd October]\-\\
	During this time period the group members will prepare the presentation of the project.
	\item[28th October]\-\\
	Until this date the final version of the document and the implementation will be delivered.
\end{description}

>>>>

Participants performed an experiment while laying in an fMRI scanner. The experiment consisted of a set of trials in which participants were presented a first stimulus for four seconds, followed by a blank screen lasting four seconds, and then a second stimulus for four seconds, followed by a rest period of 15 seconds. For the first half of the trials, a picture was presented as the first stimulus and a sentence as the second stimulus, while for the second half of trials, a sentence was presented as the first stimulus and a picture as the second. Participants had four seconds after the second stimulus appeared to indicate that the sentence and picture belonged together, after which the stimulus disappeared. If participants did not press the button the stimulus would disappear after those four seconds.

@@

\begin{description}
	\item[11th - 21st September]\-\\
	During this time period, the group members will conduct an initial research. The research will focus on the Bayes network classifiers and especially on the TAN tree algorithm. The purpose of this phase is to understand the problem.
	\item[22nd - 28th September]\-\\
	During this time period, the definition of the various models will be realised. A set of models is needed to approximate the output function.
	\item[29th - 19th October]\-\\
	Choosing and implementing a learning algorithm. This phase contains also the estimation of the parameters of the learning algorithm.
	\item[20th - 22nd October]\-\\
	During this time period the group members will prepare the presentation of the project.
	\item[28th October]\-\\
	Until this date the final version of the document and the implementation will be delivered.
\end{description}
